* **Journal Articles**

* We use rules specified here: https://med.fsu.edu/userFiles/file/AmericanMedicalAssociationStyleJAMA.pdf

We ignore:
   - Journal Supplements
   - Government Publication
   - Newspaper Article
   - Dictionary
   - Unpublished Material
   - CDROM


* We implement rules for number of authors specified [here]https://med.fsu.edu/userFiles/file/AmericanMedicalAssociationStyleJAMA.pdf
  - Two or More Works by the Same Author
    + People citing multiple retracted articles by the same author is uncommon. We leave it for later.
  - Introductions, Prefaces, Forewords, and Afterwords

* If there is a group_author, we follow advice from https://med.fsu.edu/userFiles/file/AmericanMedicalAssociationStyleJAMA.pdf


* If the article is a special issue, follow directions [here](https://med.fsu.edu/userFiles/file/AmericanMedicalAssociationStyleJAMA.pdf)

* **Online Articles**

We ignore online articles because we don't have them in our data. But the general rules are here](http://library.nymc.edu/informatics/amastyle.cfm). (We can probably safely ignore everything on the page after "Article from a Database") Add the phrase 'retrieved from' when building references. Rules for the number of authors are the same as for journal articles. 

* **Conference Papers**

We only implement rules for [Papers and Poster Sessions listed [here](https://med.fsu.edu/userFiles/file/AmericanMedicalAssociationStyleJAMA.pdf). We prepend "paper presented at" when mentioning location. If an article has both "article_title" and "conf_title", we generate two separate citations for the article---one for the conference, other for the journal article. Rules for multiple authors are the same as above.

* **Verifying Work**

We verify the references we produce by comparing against [scholar.google.com](http://scholar.google.com) and some manual sifting. We find that google scholar gets AMA citations to work with 7 or more authors incorrect.
